---
title: "Demo how to get from simple chull to ggsignif"
output: html_notebook
---



This notebook builds upon the [ggplot2 extension vignette](https://cran.r-project.org/web/packages/ggplot2/vignettes/extending-ggplot2.html).

```{r}
library(tidyverse)
```


# Template

Create a new ggproto object with the class name StatChull that inherits from `Stat`.
Other possible super-classes could be:

- ggplot2::Geom
- ggplot2::Stat
- ggplot2::Position
- or ggplot2::Scale.

```{r}
StatChull <- ggproto("StatChull", Stat,
                     compute_group = function(data, scales) {
                       data[chull(data$x, data$y), , drop = FALSE]
                     },
                     
                     required_aes = c("x", "y")
)

```

Some boilerplate to provide an easy to use function for the new StatChull layer:

```{r}
stat_chull <- function(mapping = NULL, data = NULL, geom = "polygon",
                       position = "identity", na.rm = FALSE, show.legend = NA, 
                       inherit.aes = TRUE, ...) {
  layer(
    stat = StatChull, data = data, mapping = mapping, geom = geom, 
    position = position, show.legend = show.legend, inherit.aes = inherit.aes,
    params = list(na.rm = na.rm, ...)
  )
}


```


Create a plot using the new `stat_chull`:

```{r}
ggplot(mpg, aes(displ, hwy, color=drv)) + 
  geom_point() + 
  stat_chull(fill=NA)
```


```{r}
StatChull <- ggproto("StatChull", Stat,
                     compute_group = function(data, scales) {
                       tmp <- data[chull(data$x, data$y), , drop = FALSE]
                       tmp$x <- tmp$x + 1
                       tmp
                     },
                     
                     required_aes = c("x", "y")
)

ggplot(mpg, aes(displ, hwy, color=drv)) + 
  geom_point() + 
  stat_chull(fill=NA)

```


## What is chull?

```{r}
df <- tribble(
  ~x,  ~y,
   0,   1,
   1,   0,
   0,  -1,
  -1,   0,
   0,   0
)
plot(df$x, df$y)
chull(df$x, df$y)
```



# Annotate significance in boxplot

The data

```{r}
a <- rnorm(30, mean=5, sd=1)
b <- rnorm(25, mean=6, sd=1)
df <- data_frame(Source=c(rep("A", 30), rep("B", 25)),
                 Value=c(a, b))

ggplot(df, aes(x=Source, y=Value)) + 
  geom_boxplot()
```


Manually add annotation:

```{r}
t.test(a,b)
p_value <- formatC(t.test(a, b)$p.value, digits=3)

ggplot(df, aes(x=Source, y=Value)) + 
  geom_boxplot() +
  geom_text(label=p_value, x=1.5, y=8)

```


Creating a new Stat Layer:


```{r}
StatPValue <- ggproto("StatPValue", Stat,
                     compute_group = function(data, scales) {
                       print(data)
                       stop()
                     },
                     
                     required_aes = c("x", "y")
)

stat_pvalue <- function(mapping = NULL, data = NULL, geom = "text",
                       position = "identity", na.rm = FALSE, show.legend = NA, 
                       inherit.aes = TRUE, ...) {
  layer(
    stat = StatPValue, data = data, mapping = mapping, geom = geom, 
    position = position, show.legend = show.legend, inherit.aes = inherit.aes,
    params = list(na.rm = na.rm, ...)
  )
}


ggplot(df, aes(x=Source, y=Value)) + 
  geom_boxplot() +
  stat_pvalue()

```


Use `setup_params` to access the full dataset:

```{r}
StatPValue <- ggproto("StatPValue", Stat,
                     setup_params=function(data, params){
                       params$complete_data <- data
                       return(params)
                     },
                     compute_group = function(data, scales, complete_data) {
                        p_value <- t.test(complete_data[complete_data$x == 1, "y"], 
                                          complete_data[complete_data$x == 2, "y"])$p.value
                        data.frame(label=p_value, x=1, y=1)
                     },
                     
                     required_aes = c("x", "y")
)

stat_pvalue <- function(mapping = NULL, data = NULL, geom = "text",
                       position = "identity", na.rm = FALSE, show.legend = NA, 
                       inherit.aes = TRUE, ...) {
  layer(
    stat = StatPValue, data = data, mapping = mapping, geom = geom, 
    position = position, show.legend = show.legend, inherit.aes = inherit.aes,
    params = list(na.rm = na.rm, ...)
  )
}


ggplot(df, aes(x=Source, y=Value)) + 
  geom_boxplot() +
  stat_pvalue()
```


Plot only once and fix location


```{r}
StatPValue <- ggproto("StatPValue", Stat,
                     setup_params=function(data, params){
                       params$complete_data <- data
                       return(params)
                     },
                     compute_group = function(data, scales, complete_data) {
                       if(data$group[1] == 1){
                         p_value <- t.test(complete_data[complete_data$x == 1, "y"], 
                                          complete_data[complete_data$x == 2, "y"])$p.value
                         data.frame(label=p_value, x=1.5, y=8)
                       }else{
                         data.frame(label="", x=1.5, y=8)
                       }
                     },
                     
                     required_aes = c("x", "y")
)

stat_pvalue <- function(mapping = NULL, data = NULL, geom = "text",
                       position = "identity", na.rm = FALSE, show.legend = NA, 
                       inherit.aes = TRUE, ...) {
  layer(
    stat = StatPValue, data = data, mapping = mapping, geom = geom, 
    position = position, show.legend = show.legend, inherit.aes = inherit.aes,
    params = list(na.rm = na.rm, ...)
  )
}


ggplot(df, aes(x=Source, y=Value)) + 
  geom_boxplot() +
  stat_pvalue()
```



Let the user provide the location:

```{r}
StatPValue <- ggproto("StatPValue", Stat,
                     setup_params=function(data, params){
                       params$complete_data <- data
                       return(params)
                     },
                     compute_group = function(data, scales, complete_data, loc_x, loc_y) {
                       if(data$group[1] == 1){
                         p_value <- t.test(complete_data[complete_data$x == 1, "y"], 
                                          complete_data[complete_data$x == 2, "y"])$p.value
                         data.frame(label=p_value, x=loc_x, y=loc_y)
                       }else{
                         data.frame(label="", x=loc_x, y=loc_y)
                       }
                     },
                     
                     required_aes = c("x", "y")
)

stat_pvalue <- function(loc_x, loc_y,
                       mapping = NULL, data = NULL, geom = "text",
                       position = "identity", na.rm = FALSE, show.legend = NA, 
                       inherit.aes = TRUE, ...) {
  params <- list(na.rm = na.rm, ...)
  params$loc_x <- loc_x
  params$loc_y <- loc_y
  layer(
    stat = StatPValue, data = data, mapping = mapping, geom = geom, 
    position = position, show.legend = show.legend, inherit.aes = inherit.aes,
    params = params
  )
}


ggplot(df, aes(x=Source, y=Value)) + 
  geom_boxplot() +
  stat_pvalue(loc_x=1.5, loc_y=10)
```






